An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-21 paper.tex
ignore auto/ and update julia implementation part

In order to study evolving graphs and experiment with various graph types, we have developed EvolvingGraphs.jl \cite{zhang15}, a software package in the Julia language \cite{bkse12} for the creation, manipulation, and study of dynamic networks.

In Julia,  $A_n$ is stored as an array of sparse matrices in compressed sparse column (CSC) format.

>>>>

In order to study evolving graphs and experiment with various graph types, we have developed EvolvingGraphs.jl  \cite{zhang15}, a software package in the Julia language \cite{bkse12} for the creation, manipulation, and study of dynamic networks.  
Julia is a high-level, high-performance dynamic programming language for technical
computing. When we implement EvolvingGraphs.jl, we make particular use of 
the parameterizable type system and multiple dispatch in Julia. 
We define a data type  \texttt{MatrixList}, which represents an evolving graph
as a sequence of sparse matrices stored in compressed sparse column (CSC) format. 
Many basic graph functions are defined for \texttt{MatrixList}, including 
retrieving nodes, timestamps, and matrices.
